---
title: "Eating Out"
author: "Estevan Green"
output: 
 html_document:
number_sections: true
toc: true
toc_depth: 5
date: "`r Sys.Date()`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this write up we are analyzing if there is a difference in the frequency of
eating out based on ones ethnicity.

 There were two years in which the General Social Survey asked about the frequency of eating out.

 Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then write up the answer to the question by editing the code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of  
eating out. 

$H_A$ There is a statistical difference between at least two races with the frequency of eating out


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r eval=TRUE, include=F}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```




# Method
Is there is difference based on frequency in ethnicitys in how often they eat 
out. 

# Results

## Descriptive Results

### Graphical Results 

```{r}
barchartGC(~race+eatout,data=mydata)
barchartGC(~race+eatout,data=mydata,type="percent")
```


The bar chart suggests that the white ethnicity eats out more than black and 
other ethnicity.

### Numerical Description

```{r}
table1 <- xtabs(~race+eatout,data=mydata)
rowPerc (table1)
colPerc(table1)
```
The results in this numerical description shows the frequency of 
eating out in white ethnicity as apposed to black and other ethnicity. Showing 
white ethnicity frequency of eating out is more than black and other ethnicity.


### Inferential results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```

Chi squared test shows the p value 0.0008179, we see the number is so small that
we reject the null hypothesis.

The fisherXY test for count data shows that the p value 0.001208 is also very small that we reject the null hypothesis.



# Discussion and Conclusion
Based on results, we reject the null hypothesis since the p-value is so small. Considering how small this number is 0.0008179, showing there is a difference 
in the frequency of eating out amoung the ethnicity's. 

