---
title: "Eating Out"
author: "Estevan Green"
output: 
 html_document:
number_sections: true
toc: true
toc_depth: 5
date: "`r Sys.Date()`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Is there a difference in ethnicity in how frequently they eat?

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then write up the answer to the question by editing the code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of  
eating out. 

$H_A$ There is a statistical difference between at least two races with the frequency of eating out


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r eval=TRUE, include=F}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```




# Method
the response variable (how frequently different races go out) ; the input 
variable is categorical. We have a Num ~ Cat.

# Descriptive Results

# Graphical Results 

```{r}
barchartGC(~race+eatout,data=mydata)
barchartGC(~race+eatout,data=mydata,type="percent")
```


The bar chart suggests that there is a difference in the percentage of white ethnicity to other ethnicity in eating out.

## Numerical Description

```{r}
table1 <- xtabs(~race+eatout,data=mydata)
rowPerc (table1)
colPerc(table1)
```



### Inferential results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

